Tables

### 2019-04-16 code/tables.rmd
Added tau2 from correlations to table 3

@@

#Summary of simulation results, needs to be combined with main part of table
I2_ci_lb <- dens %>% 
  bind_rows(.id = "effect") %>% 
  group_by(effect, tau_index) %>% 
  summarize(power = mean(Qp <= 0.05)) %>% #Estimate power/type 1 error for each tau level and effect
  ungroup() %>% 
  tidyr::spread(key = tau_index, value = power) %>% #prep for table
  rename(zero = '1', small = '2', medium = '3', large = '4')

#Combine dataframes to create full table
het <-  het %>% 
  left_join(I2_ci_lb) %>% 
  arrange(desc(tau2),  desc(tau2_ci.ub)) %>% #sort by tau2 and upper CI bound
  mutate(I2_ci = paste0("[", trimws(format(round(s_ci.lb, 2), nsmall = 2)), ", ", trimws(format(round(s_ci.ub, 2), nsmall = 2)), "]"), #Round and put confidence interval between brackets, e.g., [0, 0.41]
         tau2_ci = paste0("[", trimws(format(round(tau2_ci.lb, 2), nsmall = 2)), ", ", trimws(format(round(tau2_ci.ub, 2), nsmall = 2)), "]")) %>% 
  select(rp, effect, k, effect_type, eff_size, s_I2, I2_ci, tau2, tau2_ci, zero, small, medium, large)

@@

het %>% knitr::kable("latex", align = "c", booktabs = TRUE, escape = FALSE, digits = 2, col.names = c("RP", "Effect", "k", "Effect type", "Effect size estimate", "$I^2$(\\%)", "$I^2$ 95\\% CI", "$\\tau^2$", "$\\tau^2$ 95\\% CI", "Zero", "Small", "Medium", "Large")) %>% 
  add_header_above(c(" " = 9, "Level of heterogeneity" = 4)) %>% 
  add_header_above(c(" " = 9, "Type I Error Rate & Statistical Power" = 4)) %>% 
  kable_styling("scale_down", font_size = 7) %>%
  column_spec(5, width = "5em") %>% #make sure the 'Effect size estimate' header is wrapped 
  footnote(threeparttable = TRUE, escape = FALSE,
           general = "Effects were estimated in metafor using REML. The following effects are odds ratios transformed into standardized mean differences: 'Allowed vs. forbidden', 'Gain vs. loss framing', 'Norm of reciprocity', 'Low vs. high category scales'. RP = Replication Project, k = no. primary studies, CI = confidence intervals. Statistical power and type I error rates were simulated, where Zero = simulated type 1 error, and the other headers represent simulated power under small/medium/large heterogeneity ($I^2$ = 25/50/75\\\\%) respectively. SMD = Standardized Mean difference (Hedge's g), MD = Mean Difference, RD = Risk Difference, r = correlation. Code to reproduce table: osf.io/kf6pt/",
           alphabet = "These effects were simulated as standardized mean differences") %>% 
  landscape()

>>>>

#Transform effect sizes to raw correlations
#'transform_MA' is a sourced function
dat2 <- dat %>% 
  split(.$effect) %>%  #separate by effect, necessary step otherwise the function is applied overall
  map_dfr(transform_MA, .id = "effect") #apply function and transform back from list to dataframe

summarizer <- function(x){ #function to run rma on transformed biserial and correlations
  fitr <- rma(yi = x$r, vi = x$vi, data = x) #rma for biserial and pearson correlations (distinct per effect!)
  ci <- confint(fitr)$random[c(1, 3), ]
  data.frame(r = fitr$b[[1]], tau2 = fitr$tau2, tau2.lb = ci[1, 2], tau2.ub = ci[1, 3],
             I2 = fitr$I2, I2.lb = ci[2, 2], I2.ub = ci[2, 3]) 
}

#estimate tau2 for tranformed biserial and pearson's correlations
res2 <- dat2 %>% 
  split(.$effect) %>%  #separate by effect, necessary step otherwise the function is applied overall
  map_dfr(summarizer, .id = "effect")

#NB! note that for low vs. high category scales, the I2 lower bound is zero, but after transformation
#the tau2 lower bound is *not* zero. This is an indication of the problems with effect size tranformations.

res <- res %>%
  mutate(tau2 = res2$tau2, #For table 3, report tau2 and transformed effect sizes (biserial correlations)
         tau2_ci.lb = res2$tau2.lb,
         tau2_ci.ub = res2$tau2.ub,
         r = res2$r)

@@

#Summary of simulation results, needs to be combined with main part of table
I2_power <- dens %>% 
  bind_rows(.id = "effect") %>% 
  group_by(effect, tau_index) %>% 
  summarize(power = mean(Qp <= 0.05)) %>% #Estimate power/type 1 error for each tau level and effect
  ungroup() %>% 
  tidyr::spread(key = tau_index, value = power) %>% #prep for table
  rename(zero = '1', small = '2', medium = '3', large = '4')

#Combine dataframes to create full table
het <-  het %>% 
  left_join(I2_power) %>% 
  arrange(desc(s_I2),  desc(s_ci.ub)) %>% #sort by tau2 and upper CI bound
  mutate(I2_ci = paste0("[", trimws(format(round(s_ci.lb, 2), nsmall = 2)), ", ", trimws(format(round(s_ci.ub, 2), nsmall = 2)), "]"), #Round and put confidence interval between brackets, e.g., [0, 0.41]
         tau2_ci = paste0("[", trimws(format(round(tau2_ci.lb, 2), nsmall = 2)), ", ", trimws(format(round(tau2_ci.ub, 2), nsmall = 2)), "]")) %>% 
  select(rp, effect, k, effect_type, eff_size, s_I2, I2_ci, r, tau2, tau2_ci, zero, small, medium, large)

@@

het %>% knitr::kable("latex", align = "c", booktabs = TRUE, escape = FALSE, digits = 2, col.names = c("RP", "Effect", "K", "Effect type", "Effect size estimate",  "$I^2$(\\%)", "$I^2$ 95\\% CI", "r*" , "$\\tau^2$", "$\\tau^2$ 95\\% CI", "Zero", "Small", "Medium", "Large")) %>% 
  add_header_above(c(" " = 10, "Level of heterogeneity" = 4)) %>% 
  add_header_above(c(" " = 10, "Type I Error Rate & Statistical Power" = 4)) %>% 
  kable_styling("scale_down", font_size = 7) %>%
  column_spec(5, width = "5em") %>% #make sure the 'Effect size estimate' header is wrapped 
  footnote(threeparttable = TRUE, escape = FALSE,
           general = "Effects were estimated in metafor using REML. The following effects are odds ratios transformed into standardized mean differences: 'Allowed vs. forbidden', 'Gain vs. loss framing', 'Norm of reciprocity', 'Low vs. high category scales'. RP = Replication Project, k = no. primary studies, CI = confidence intervals, r* = effect sizes as correlations and biserial correlations. Statistical power and type I error rates were simulated, where Zero = simulated type 1 error, and the other headers represent simulated power under small/medium/large heterogeneity ($I^2$ = 25/50/75\\\\%) respectively. SMD = Standardized Mean difference (Hedge's g), MD = Mean Difference, RD = Risk Difference, r = correlation. Code to reproduce table: osf.io/kf6pt/",
           alphabet = "These effects were simulated as standardized mean differences") %>% 
  landscape()
